---
title: "Social Doors RSA"
author: "Haroon Popal"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    number_sections: true
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 2
    df_print: paged
    css: !expr here::here("./code/style_srk_behavioral.css")
    knit: (function(inputFile, encoding) { 
      out_dir <- './';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'index.html')) })
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

require("knitr")
opts_knit$set(root.dir = "~/OneDrive - Temple University/olson_lab/projects/social_doors/derivatives/rsa-bw_runs-fb_only/")
```


```{r}
library(ggplot2)
library(dplyr)
library(reshape2)
library(psych)
library(ggpubr)
library(stringr)
library(kableExtra)
```

```{r}
conds <- c('negative_win-mdoors', 'negative_loss-mdoors',
           'positive_win-mdoors', 'positive_loss-mdoors',
           'negative_win-social', 'negative_loss-social',
           'positive_win-social', 'positive_loss-social')

n_conds <- length(conds)
```



# Model RDMs

## Task Domain

```{r}
rdm_tdomain <- c(c(0,0,0,0,1,1,1,1),
                 c(0,0,0,0,1,1,1,1),
                 c(0,0,0,0,1,1,1,1),
                 c(0,0,0,0,1,1,1,1),
                 c(1,1,1,1,0,0,0,0),
                 c(1,1,1,1,0,0,0,0),
                 c(1,1,1,1,0,0,0,0),
                 c(1,1,1,1,0,0,0,0))

dim(rdm_tdomain) <- c(n_conds, n_conds)

dimnames(rdm_tdomain) = list(conds, conds)

rdm_tdomain_melt <- melt(rdm_tdomain)

ggplot(rdm_tdomain_melt, aes(x=Var1, y=ordered(Var2, levels = rev(sort(unique(Var2)))), fill=value)) +
  geom_tile(width = 1, color = 'grey') +
  theme_minimal() + 
  scale_fill_distiller(palette = "Oranges", direction = 1) + 
  labs(title = "Task Domain RDM", x = "\nTask Conditions", y = "", fill = 'Dissimilarity') + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", angle = 45, vjust = 0.5),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), plot.background = element_blank())

ggsave('rdm_tdomain.png')
```

## Valence
```{r}
rdm_valence <- c(c(0,0,1,1,0,0,1,1),
                 c(0,0,1,1,0,0,1,1),
                 c(1,1,0,0,1,1,0,0),
                 c(1,1,0,0,1,1,0,0),
                 c(0,0,1,1,0,0,1,1),
                 c(0,0,1,1,0,0,1,1),
                 c(1,1,0,0,1,1,0,0),
                 c(1,1,0,0,1,1,0,0))

dim(rdm_valence) <- c(n_conds, n_conds)

dimnames(rdm_valence) = list(conds, conds)

rdm_valence_melt <- melt(rdm_valence)

ggplot(rdm_valence_melt, aes(x=Var1, y=ordered(Var2, levels = rev(sort(unique(Var2)))), fill=value)) +
  geom_tile(width = 1, color = 'grey') +
  theme_minimal() + 
  scale_fill_distiller(palette = "Oranges", direction = 1) + 
  labs(title = "Valence RDM", x = "\nTask Conditions", y = "", fill = 'Dissimilarity') + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", angle = 45, vjust = 0.5),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), plot.background = element_blank())

ggsave('rdm_valence.png')
```


## Outcome
```{r}
rdm_outcome = c(c(0,1,0,1,0,1,0,1),
                c(1,0,1,0,1,0,1,0),
                c(0,1,0,1,0,1,0,1),
                c(1,0,1,0,1,0,1,0),
                c(0,1,0,1,0,1,0,1),
                c(1,0,1,0,1,0,1,0),
                c(0,1,0,1,0,1,0,1),
                c(1,0,1,0,1,0,1,0))

dim(rdm_outcome) <- c(n_conds, n_conds)

dimnames(rdm_outcome) = list(conds, conds)

rdm_outcome_melt <- melt(rdm_outcome)

ggplot(rdm_outcome_melt, aes(x=Var1, y=ordered(Var2, levels = rev(sort(unique(Var2)))), fill=value)) +
  geom_tile(width = 1, color = 'grey') +
  theme_minimal() + 
  scale_fill_distiller(palette = "Oranges", direction = 1) + 
  labs(title = "Outcome RDM", x = "\nTask Conditions", y = "", fill = 'Dissimilarity') + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", angle = 45, vjust = 0.5),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), plot.background = element_blank())

ggsave('rdm_outcome.png')
```


## Outcome Valence
Being correct about someone not liking you is different from being correct about someone liking you. But being incorrect about someone not liking you is the same feeling as being incorrect about someone not liking out (negative).
```{r}
rdm_outcval = c(c(1,1,1,1,1,1,1,1),
                c(1,0,1,0,1,0,1,0),
                c(1,1,1,1,1,1,1,1),
                c(1,0,1,0,1,0,1,0),
                c(1,1,1,1,1,1,1,1),
                c(1,0,1,0,1,0,1,0),
                c(1,1,1,1,1,1,1,1),
                c(1,0,1,0,1,0,1,0))

dim(rdm_outcval) <- c(n_conds, n_conds)

dimnames(rdm_outcval) = list(conds, conds)

rdm_outcval_melt <- melt(rdm_outcval)

ggplot(rdm_outcval_melt, aes(x=Var1, y=ordered(Var2, levels = rev(sort(unique(Var2)))), fill=value)) +
  geom_tile(width = 1, color = 'grey') +
  theme_minimal() + 
  scale_fill_distiller(palette = "Oranges", direction = 1) + 
  labs(title = "Outcome Valence RDM", x = "\nTask Conditions", y = "", fill = 'Dissimilarity') + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", angle = 45, vjust = 0.5),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), plot.background = element_blank())

ggsave('rdm_outcval.png')
```


## Interaction
Being correct about someone not liking you is different from being correct about someone liking you. But being incorrect about someone not liking you is the same feeling as being incorrect about someone not liking out (negative).
```{r}
rdm_intract = c(c(0/3, 1/3, 1/3, 2/3, 1/3, 2/3, 2/3, 3/3),
                c(1/3, 0/3, 2/3, 1/3, 2/3, 1/3, 3/3, 2/3),
                c(1/3, 2/3, 0/3, 1/3, 2/3, 3/3, 1/3, 2/3),
                c(2/3, 1/3, 1/3, 0/3, 3/3, 2/3, 2/3, 1/3),
                c(1/3, 2/3, 2/3, 3/3, 0/3, 1/3, 1/3, 2/3),
                c(2/3, 1/3, 3/3, 2/3, 1/3, 0/3, 2/3, 1/3),
                c(2/3, 3/3, 1/3, 2/3, 1/3, 2/3, 0/3, 1/3),
                c(3/3, 2/3, 2/3, 1/3, 2/3, 1/3, 1/3, 0/3))

dim(rdm_intract) <- c(n_conds, n_conds)

dimnames(rdm_intract) = list(conds, conds)

rdm_intract_melt <- melt(rdm_intract)

ggplot(rdm_intract_melt, aes(x=Var1, y=ordered(Var2, levels = rev(sort(unique(Var2)))), fill=value)) +
  geom_tile(width = 1, color = 'grey') +
  theme_minimal() + 
  scale_fill_distiller(palette = "Oranges", direction = 1) + 
  labs(title = "Valence Outcome Interaction RDM", x = "\nTask Conditions", y = "", fill = 'Dissimilarity') + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", angle = 45, vjust = 0.5),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), plot.background = element_blank())

ggsave('rdm_intract.png')
```


### Define Hypothesized ROIs
```{r}
hyp_rois <- c('TPJ_b-social', 'dmPFC_b-social',
              'region08', 'region06',
              'striatum_ventral',
              'region02')
hyp_rois_names <- c('TPJ', 'dmPFC',
                    'CB Region 8','CB Region 6',
                    'Ventral Striatum',
                    'CB Region 2')
```


### Define color palette for plots
```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

```









***
# Representational Similarity Analysis


# Positive win is different from negative win
```{r}
all_sim_vcr <- read.csv(file='posnegwin_similarity.csv', header = TRUE)
all_sim_vcr
```


```{r}
# Use "adult as group label
all_sim_vcr$group[all_sim_vcr$group == 'control'] <- 'adult'
all_sim_vcr$group[all_sim_vcr$group == 'college'] <- 'adult'
```



Divide data by task
```{r}
all_sim_vcr_mdoors <- all_sim_vcr[all_sim_vcr$task %in% 'mdoors', ]
all_sim_vcr_social <- all_sim_vcr[all_sim_vcr$task %in% 'social', ]

```

Filter data by hypothesized ROIs
```{r}
#hyp_rois <- c('striatum_ventral','striatum_dorsalp','region08','region02','TPJ_b-social')

all_sim_vcr_mdoors_rois <- all_sim_vcr_mdoors[all_sim_vcr_mdoors$roi %in% hyp_rois, ]
all_sim_vcr_social_rois <- all_sim_vcr_social[all_sim_vcr_social$roi %in% hyp_rois, ]
#all_sim_vcr_social_rois$roi <- factor(all_sim_vcr_social_rois$roi, levels=hyp_rois)

```


Fischer r to z transform
```{r}
all_sim_vcr_mdoors_rois$z <- fisherz(all_sim_vcr_mdoors_rois$r)
all_sim_vcr_social_rois$z <- fisherz(all_sim_vcr_social_rois$r)

```




```{r}

all_sim_vcr_mdoors_rois.ttests <- data.frame(matrix(ncol=7,nrow=0))
all_sim_vcr_social_rois.ttests <- data.frame(matrix(ncol=7,nrow=0))
colnames(all_sim_vcr_mdoors_rois.ttests) <- c('roi','t_stat','p','estimate','CI_l','CI_h','df')
colnames(all_sim_vcr_social_rois.ttests) <- c('roi','t_stat','p','estimate','CI_l','CI_h','df')

row_n = 1
for (roi in hyp_rois) {
  # Filter for ROI data
  roi_data_mdoors <- all_sim_vcr_mdoors_rois[all_sim_vcr_mdoors_rois$roi %in% roi, ]
  roi_data_social <- all_sim_vcr_social_rois[all_sim_vcr_social_rois$roi %in% roi, ]
  
  # Calculate t-test
  temp_ttest_mdoors <- t.test(roi_data_mdoors$r, mu=0)
  temp_ttest_social <- t.test(roi_data_social$r, mu=0)
  
  # Fill in dataframe
  all_sim_vcr_mdoors_rois.ttests[row_n,] <- c(roi,temp_ttest_mdoors$statistic,
                                              temp_ttest_mdoors$p.value,
                                              temp_ttest_mdoors$estimate, 
                                              temp_ttest_mdoors$conf.int[1],
                                              temp_ttest_mdoors$conf.int[2],
                                              temp_ttest_mdoors$parameter[[1]])
  all_sim_vcr_social_rois.ttests[row_n,] <- c(roi,temp_ttest_social$statistic,
                                              temp_ttest_social$p.value,
                                              temp_ttest_social$estimate, 
                                              temp_ttest_social$conf.int[1],
                                              temp_ttest_social$conf.int[2],
                                              temp_ttest_social$parameter[[1]])
      
  # Increase counter for row numbers
      
  row_n = row_n+1
}

all_sim_vcr_mdoors_rois.ttests$p_adjust <- p.adjust(all_sim_vcr_mdoors_rois.ttests$p,
                                                   method='fdr')
all_sim_vcr_social_rois.ttests$p_adjust <- p.adjust(all_sim_vcr_social_rois.ttests$p,
                                                   method='fdr')

```


## Monetary

### ANOVA
```{r}
anova_mod_sim_vcr <- aov(r ~ roi, data=all_sim_vcr_mdoors_rois)
summary(anova_mod_sim_vcr)
```



```{r}
x <- all_sim_vcr_mdoors_rois$r
factor <- all_sim_vcr_mdoors_rois$roi

mean.sd <- function(x) c(mean = mean(x), sd = sd(x))
simplify2array(tapply(x, factor, mean.sd))
```


## Post-hoc Tests
```{r}
tukey.test <- TukeyHSD(anova_mod_sim_vcr)
tukey.test
```

```{r}
stats <- compare_means(r ~ roi, , data = all_sim_vcr_mdoors_rois, method = "t.test",
                       p.adjust.method = 'fdr')
stats
```

```{r}
P_adjust <- all_sim_vcr_mdoors_rois.ttests$p_adjust
Sig_adjust = ifelse(P_adjust < 0.005, "***", ifelse(P_adjust < 0.01, "**", 
                                             ifelse(P_adjust < 0.05, "*", "")))

p <- ggbarplot(all_sim_vcr_mdoors_rois, x = 'roi', 
               y = 'r', add = 'mean_se',
               fill=cbPalette[6],
               position = position_dodge(0.8))
p + theme(axis.text.x = element_text(angle =45, vjust = 0.5)) + 
  geom_signif(comparisons = list(c("region08", "striatum_ventral")),
              map_signif_level = TRUE,
              annotations = c('*'), y_position = c(0.075,0.095), vjust=0.1) + 
  #scale_x_discrete(labels=hyp_rois_names) + 
  xlab("Regions of Interests") + ylab("Spearman's rho") + 
  ggtitle("Positive and Negative Win Similarity in Monetary Task") 

ggsave('rsa_vcr_mdoors.png')

```



### One sample t-tests
#### Right Crus I
```{r}
roi_c1_r <- all_sim_vcr_mdoors[all_sim_vcr_mdoors$roi == 'region08',]$r
roi_c1_z <- fisherz(roi_c1_r)
t.test(roi_c1_z, mu = 0)
```


#### Bilateral Ventrial Striatum
```{r}
roi_VS_b <- all_sim_vcr_mdoors[all_sim_vcr_mdoors$roi == 'striatum_ventral',]$r
roi_VS_z <- fisherz(roi_VS_b)
t.test(roi_VS_z, mu = 0)
```



## Social

### ANOVA
```{r}
anova_mod_sim_vcr <- aov(r ~ roi, data=all_sim_vcr_social_rois)
summary(anova_mod_sim_vcr)
```

```{r}
x <- all_sim_vcr_social_rois$r
factor <- all_sim_vcr_social_rois$roi

mean.sd <- function(x) c(mean = mean(x), sd = sd(x))
simplify2array(tapply(x, factor, mean.sd))
```

```{r}
tapply(x, factor, sd)
```




## Post-hoc Tests
```{r}
tukey.test <- TukeyHSD(anova_mod_sim_vcr)
tukey.test
```



```{r}
stats <- compare_means(r ~ roi, , data = all_sim_vcr_social_rois, method = "t.test",
                       p.adjust.method = 'fdr')
stats
```




```{r}

P_adjust <- all_sim_vcr_social_rois.ttests$p_adjust
Sig_adjust = ifelse(P_adjust < 0.005, "***", ifelse(P_adjust < 0.01, "**", 
                                             ifelse(P_adjust < 0.05, "*", "")))

p <- ggbarplot(all_sim_vcr_social_rois, x = 'roi', 
               y = 'r', add = 'mean_se',
               fill=cbPalette[6],
               position = position_dodge(0.8))
p + theme(axis.text.x = element_text(angle =45, vjust = 0.5)) + 
  #geom_signif(comparisons = list(c("region08", "striatum_ventral"),
  #                               c('region08','striatum_dorsalp'),
  #                               c('region08','region02'),
  #                               c('region08','TPJ_b-social')),
  #            map_signif_level = TRUE,
  #            annotations = c('***','***','*','*'), 
  #            y_position = c(0.155,0.18,0.13,0.205), vjust=0.1) + 
  #scale_x_discrete(labels=hyp_rois_names) + 
  xlab("Regions of Interests") + ylab("Spearman's rho") + 
  ggtitle("Positive and Negative Win Similarity in Social Task")
ggsave('rsa_vcr_social.png')

```



### One sample t-tests
#### Right Crus I
```{r}
roi_c1_r <- all_sim_vcr_social[all_sim_vcr_social$roi == 'region08',]$r
roi_c1_z <- fisherz(roi_c1_r)
t.test(roi_c1_z, mu = 0)
```


#### Bilateral Ventrial Striatum
```{r}
roi_VS_b <- all_sim_vcr_social[all_sim_vcr_social$roi == 'striatum_ventral',]$r
roi_VS_z <- fisherz(roi_VS_b)
t.test(roi_VS_z, mu = 0)
```











## Task Domain
```{r}
# Import data
data_tdomain <- read.csv(file='tdomain_rdm_similarity.csv', header = TRUE)

# Use "adult as group label
data_tdomain$group[data_tdomain$group == 'control'] <- 'adult'
data_tdomain$group[data_tdomain$group == 'college'] <- 'adult'

head(data_tdomain)
```


Filter data by hypothesized ROIs
```{r}

data_tdomain_rois <- data_tdomain[data_tdomain$roi %in% hyp_rois, ]

```




```{r}

data_tdomain_rois.ttests <- data.frame(matrix(ncol=7,nrow=0))
colnames(data_tdomain_rois.ttests) <- c('roi','t_stat','p','estimate','CI_l','CI_h','df')

row_n = 1
for (roi in hyp_rois) {
  # Filter for ROI data
  roi_data <- data_tdomain_rois[data_tdomain_rois$roi %in% roi, ]

  # Calculate t-test
  temp_ttest <- t.test(roi_data$r, mu=0)

  # Fill in dataframe
  data_tdomain_rois.ttests[row_n,] <- c(roi,temp_ttest$statistic,
                                              temp_ttest$p.value,
                                              temp_ttest$estimate, 
                                              temp_ttest$conf.int[1],
                                              temp_ttest$conf.int[2],
                                              temp_ttest$parameter[[1]])

      
  # Increase counter for row numbers
      
  row_n = row_n+1
}

data_tdomain_rois.ttests$p_adjust <- p.adjust(data_tdomain_rois.ttests$p,
                                                   method='fdr')

```



### ANOVA
```{r}
anova_mod_tdomain <- aov(r ~ roi, data=data_tdomain_rois)
summary(anova_mod_tdomain)
```


```{r}
x <- data_tdomain_rois$r
factor <- data_tdomain_rois$roi

mean.sd <- function(x) c(mean = mean(x), sd = sd(x))
simplify2array(tapply(x, factor, mean.sd))
```


### Post-hoc Tests
```{r}
tukey.test <- TukeyHSD(anova_mod_tdomain)
tukey.test
```


```{r}
stats <- compare_means(r ~ roi, , data = data_tdomain_rois, method = "t.test",
                       p.adjust.method = 'fdr')
stats
```


### Visualization
```{r}

p <- ggbarplot(data_tdomain_rois, x = 'roi', 
               y = 'r', add = 'mean_se',
               fill=cbPalette[7],
               position = position_dodge(0.8))
p + theme(axis.text.x = element_text(angle =45, vjust = 0.5)) + 
  #geom_signif(comparisons = list(c("region06", "striatum_ventral"),
  #                               c('region06','striatum_dorsalp')),
  #            map_signif_level = TRUE,
  #            annotations = c('***','*'), y_position = c(0.166,0.185), vjust=0.1) + 
  #scale_x_discrete(labels=hyp_rois_names) + 
  xlab("Regions of Interests") + ylab("Spearman's rho") + 
  ggtitle("Similarity to Task Domain RDM") 

ggsave('rsa_tdomain.png')

```




### Create function for t-tests, ANOVA
```{r}
calculate_rsa_stats <- function(data_df_rois) {
  # Calculate one-sample t-tests
  data_df_rois.ttests <- data.frame(matrix(ncol=7,nrow=0))
  colnames(data_df_rois.ttests) <- c('roi','t_stat','p','estimate','CI_l','CI_h','df')
  
  row_n = 1
  for (roi in hyp_rois) {
    # Filter for ROI data
    roi_data <- data_df_rois[data_df_rois$roi %in% roi, ]
  
    # Calculate t-test
    temp_ttest <- t.test(roi_data$r, mu=0)
  
    # Fill in dataframe
    data_df_rois.ttests[row_n,] <- c(roi,temp_ttest$statistic,
                                                temp_ttest$p.value,
                                                temp_ttest$estimate, 
                                                temp_ttest$conf.int[1],
                                                temp_ttest$conf.int[2],
                                                temp_ttest$parameter[[1]])
  
        
    # Increase counter for row numbers
        
    row_n = row_n+1
  }
  
  data_df_rois.ttests$p_adjust <- p.adjust(data_df_rois.ttests$p,
                                                     method='fdr')
  
  return(data_df_rois.ttests)
  
}
```



## Valence
```{r}
# Import data
data_valence <- read.csv(file='valence_rdm_similarity.csv', header = TRUE)

# Use "adult as group label
data_valence$group[data_valence$group == 'control'] <- 'adult'
data_valence$group[data_valence$group == 'college'] <- 'adult'

# Filter for hypothesized rois
data_valence_rois <- data_valence[data_valence$roi %in% hyp_rois, ]

data_valence_rois.ttests <- calculate_rsa_stats(data_valence_rois)

```


### ANOVA
```{r}
anova_mod_valence <- aov(r ~ roi, data=data_valence_rois)
summary(anova_mod_valence)
```


```{r}
x <- data_valence_rois$r
factor <- data_valence_rois$roi

mean.sd <- function(x) c(mean = mean(x), sd = sd(x))
simplify2array(tapply(x, factor, mean.sd))
```


### Post-hoc Tests
```{r}
tukey.test <- TukeyHSD(anova_mod_valence)
tukey.test
```


```{r}
stats <- compare_means(r ~ roi, , data = data_valence_rois, method = "t.test",
                       p.adjust.method = 'fdr')
head(stats)
```


### Visualization
```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

p <- ggbarplot(data_valence_rois, x = 'roi', 
               y = 'r', add = 'mean_se',
               fill=cbPalette[7],
               position = position_dodge(0.8))
p + theme(axis.text.x = element_text(angle =45, vjust = 0.5)) + 
  #geom_signif(comparisons = list(c("region06", "striatum_ventral"),
  #                               c('region06','striatum_dorsalp')),
  #            map_signif_level = TRUE,
  #            annotations = c('***','*'), y_position = c(0.166,0.185), vjust=0.1) + 
  #scale_x_discrete(labels=hyp_rois_names) + 
  xlab("Regions of Interests") + ylab("Spearman's rho") + 
  ggtitle("Similarity to Valence RMD") 

ggsave('rsa_valence.png')

```



## Outcome
```{r}
# Import data
data_outcome <- read.csv(file='outcome_rdm_similarity.csv', header = TRUE)

# Use "adult as group label
data_outcome$group[data_outcome$group == 'control'] <- 'adult'
data_outcome$group[data_outcome$group == 'college'] <- 'adult'

# Filter for hypothesized rois
data_outcome_rois <- data_outcome[data_outcome$roi %in% hyp_rois, ]

data_outcome_rois.ttests <- calculate_rsa_stats(data_outcome_rois)

```


### ANOVA
```{r}
anova_mod_outcome <- aov(r ~ roi, data=data_outcome_rois)
summary(anova_mod_outcome)
```


```{r}
x <- data_outcome_rois$r
factor <- data_outcome_rois$roi

mean.sd <- function(x) c(mean = mean(x), sd = sd(x))
simplify2array(tapply(x, factor, mean.sd))
```


## Post-hoc Tests
```{r}
tukey.test <- TukeyHSD(anova_mod_outcome)
tukey.test
```


```{r}
stats <- compare_means(r ~ roi, , data = data_outcome_rois, method = "t.test",
                       p.adjust.method = 'fdr')
head(stats)
```


### Visualization
```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

p <- ggbarplot(data_outcome_rois, x = 'roi', 
               y = 'r', add = 'mean_se',
               fill=cbPalette[7],
               position = position_dodge(0.8))
p + theme(axis.text.x = element_text(angle =45, vjust = 0.5)) + 
  #geom_signif(comparisons = list(c("region06", "striatum_ventral"),
  #                               c('region06','striatum_dorsalp')),
  #            map_signif_level = TRUE,
  #            annotations = c('***','*'), y_position = c(0.166,0.185), vjust=0.1) + 
  #scale_x_discrete(labels=hyp_rois_names) + 
  xlab("Regions of Interests") + ylab("Spearman's rho") + 
  ggtitle("Similarity to Outcome RMD") 

ggsave('rsa_outcome.png')

```



## Outcome Valence
```{r}
# Import data
data_outcval <- read.csv(file='crctval_rdm_similarity.csv', header = TRUE)

# Use "adult as group label
data_outcval$group[data_outcval$group == 'control'] <- 'adult'
data_outcval$group[data_outcval$group == 'college'] <- 'adult'

# Filter for hypothesized rois
data_outcval_rois <- data_outcval[data_outcval$roi %in% hyp_rois, ]

data_outcval_rois.ttests <- calculate_rsa_stats(data_outcval_rois)

```


### ANOVA
```{r}
anova_mod_outcval <- aov(r ~ roi, data=data_outcval_rois)
summary(anova_mod_outcval)
```


```{r}
x <- data_outcval_rois$r
factor <- data_outcval_rois$roi

mean.sd <- function(x) c(mean = mean(x), sd = sd(x))
simplify2array(tapply(x, factor, mean.sd))
```


### Post-hoc Tests
```{r}
tukey.test <- TukeyHSD(anova_mod_outcval)
tukey.test
```


```{r}
stats <- compare_means(r ~ roi, , data = data_outcval_rois, method = "t.test",
                       p.adjust.method = 'fdr')
head(stats)
```


### Visualization
```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

p <- ggbarplot(data_outcval_rois, x = 'roi', 
               y = 'r', add = 'mean_se',
               fill=cbPalette[7],
               position = position_dodge(0.8))
p + theme(axis.text.x = element_text(angle =45, vjust = 0.5)) + 
  #geom_signif(comparisons = list(c("region06", "striatum_ventral"),
  #                               c('region06','striatum_dorsalp')),
  #            map_signif_level = TRUE,
  #            annotations = c('***','*'), y_position = c(0.166,0.185), vjust=0.1) + 
  #scale_x_discrete(labels=hyp_rois_names) + 
  xlab("Regions of Interests") + ylab("Spearman's rho") + 
  ggtitle("Similarity to Outcome Valence RMD") 

ggsave('rsa_outcval.png')

```



## Outcome Valence Interaction
```{r}
# Import data
data_intract <- read.csv(file='intract_rdm_similarity.csv', header = TRUE)

# Use "adult as group label
data_intract$group[data_intract$group == 'control'] <- 'adult'
data_intract$group[data_intract$group == 'college'] <- 'adult'

# Filter for hypothesized rois
data_intract_rois <- data_intract[data_intract$roi %in% hyp_rois, ]

data_intract_rois.ttests <- calculate_rsa_stats(data_intract_rois)

```


### ANOVA
```{r}
anova_mod_intract <- aov(r ~ roi, data=data_intract_rois)
summary(anova_mod_intract)
```


```{r}
x <- data_intract_rois$r
factor <- data_intract_rois$roi

mean.sd <- function(x) c(mean = mean(x), sd = sd(x))
simplify2array(tapply(x, factor, mean.sd))
```


### Post-hoc Tests
```{r}
tukey.test <- TukeyHSD(anova_mod_intract)
tukey.test
```


```{r}
stats <- compare_means(r ~ roi, , data = data_intract_rois, method = "t.test",
                       p.adjust.method = 'fdr')
head(stats)
```


# Visualization
```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

p <- ggbarplot(data_intract_rois, x = 'roi', 
               y = 'r', add = 'mean_se',
               fill=cbPalette[7],
               position = position_dodge(0.8))
p + theme(axis.text.x = element_text(angle =45, vjust = 0.5)) + 
  #geom_signif(comparisons = list(c("region06", "striatum_ventral"),
  #                               c('region06','striatum_dorsalp')),
  #            map_signif_level = TRUE,
  #            annotations = c('***','*'), y_position = c(0.166,0.185), vjust=0.1) + 
  #scale_x_discrete(labels=hyp_rois_names) + 
  xlab("Regions of Interests") + ylab("Spearman's rho") + 
  ggtitle("Similarity to Outcome Valence Interaction RMD") 

ggsave('rsa_intract.png')

```






***



## Combine one-sample t-test data
```{r}
data_tdomain_rois.ttests$source <- 'tdomain'
data_valence_rois.ttests$source <- 'valence'
data_outcome_rois.ttests$source <- 'outcome'
data_outcval_rois.ttests$source <- 'outcval'
data_intract_rois.ttests$source <- 'intract'

all_sim_vcr_mdoors_rois.ttests$source <- 'vcr_mdoors'
all_sim_vcr_social_rois.ttests$source <- 'vcr_social'


one_sample_ttests <- rbind(data_tdomain_rois.ttests,
                           data_valence_rois.ttests,
                           data_outcome_rois.ttests,
                           data_outcval_rois.ttests,
                           data_intract_rois.ttests,
                           all_sim_vcr_mdoors_rois.ttests, 
                           all_sim_vcr_social_rois.ttests)

```

Fix up dataframe for pretty table
```{r}
# Sort dataframe
one_sample_table <- one_sample_ttests[order(one_sample_ttests$source, one_sample_ttests$roi), ]

# Rename ROI names
rep_str = c('region02'='CB Region 2','region08'='CB Region 8',
            'striatum_dorsalp'='Posterior Dorsal Striatum','striatum_ventral'='Ventral Striatum',
            'TPJ_b-social'='TPJ')
one_sample_table$roi <- str_replace_all(one_sample_table$roi, rep_str)

# Turn columns numeric
one_sample_table$t_stat <- as.numeric(one_sample_table$t_stat)
one_sample_table$estimate <- as.numeric(one_sample_table$estimate)
one_sample_table$CI_l <- as.numeric(one_sample_table$CI_l)
one_sample_table$CI_h <- as.numeric(one_sample_table$CI_h)
one_sample_table$p_adjust <- as.numeric(one_sample_table$p_adjust)

# Round numbers
one_sample_table$t_stat <- round(one_sample_table$t_stat,2)
one_sample_table$estimate <- round(one_sample_table$estimate,2)
one_sample_table$CI_l <- round(one_sample_table$CI_l,2)
one_sample_table$CI_h <- round(one_sample_table$CI_h,2)
one_sample_table$p_adjust <- round(one_sample_table$p_adjust,3)

# Combine confidence inverval ranges
one_sample_table$CI <- paste('[', as.character(one_sample_table$CI_l),
                              ', ', as.character(one_sample_table$CI_h), ']')

# Reorder columns
one_sample_table <- one_sample_table[, c("roi", "estimate", "df", "t_stat",
                                           "p_adjust", "CI")]

colnames(one_sample_table) <- c('ROI','Mean','df','t-statistic','p','CI')

```

```{r}
one_sample_table %>%
  kbl(caption = "RSA results for a full and partial similarity analysis") %>%
  kable_classic(full_width = F, html_font = "Times New Roman") %>%
  save_kable("one_sample_ttests.html")


one_sample_table %>%
  kbl(caption = "RSA results for a full and partial similarity analysis") %>%
  kable_classic(full_width = F, html_font = "Times New Roman")
```



---

# Behavioral Analysis
Research Question: Does greater similarity for positive and negative wins relate to anxiety and depression?

Hypothesis 1: Greater similarity between positive and negative wins in the ventral striatum will be related to greater anxiety and less depression
(Quarmley replication)

Hypothesis 2: Greater similarity between positive and negative wins in the cerebellum ...

```{r}
library(readxl)
library(dplyr)
```


```{r}
full_data <- read.csv('../../misc/aggregate_paper_data_SPSS_020419.csv')

full_data$Subject <- gsub('s', 'sub-', full_data$Subject)

# Rename subject column name
colnames(full_data)[colnames(full_data) == 'Subject'] <- 'subject_id'

full_data
```


## Hypothesis 1 testing

```{r}
vs_vcr_social <- all_sim_vcr_social_rois[all_sim_vcr_social_rois$roi %in% 'region08',]

# Rename subject column name
colnames(vs_vcr_social)[colnames(vs_vcr_social) == 'subj'] <- 'subject_id'

vs_vcr_social_behav <- merge(vs_vcr_social,full_data, by='subject_id')

# Filter for just the kids
vs_vcr_social_behav <- vs_vcr_social_behav[vs_vcr_social_behav$group %in% 'kid',]

# Bin depression in low and high groups
vs_vcr_social_behav <- vs_vcr_social_behav %>% mutate(dep_group = case_when(ch_cdi_total >= 9 ~ 'high',
                                                                            ch_cdi_total < 9 ~ 'low'))

# Filter for relevant variables
vs_vcr_social_fltr <- vs_vcr_social_behav[c('subject_id','z','ch_totanx','dep_group')]


```

```{r}
anova_mod_vs_sim <- aov(z ~ ch_totanx*dep_group, data=vs_vcr_social_fltr)
summary(anova_mod_vs_sim)
```


```{r}
lm_vs_sim <- aov(z ~ ch_totanx, data=vs_vcr_social_fltr)
summary(lm_vs_sim)
```


```{r}
ggplot(data=vs_vcr_social_fltr,aes(x=ch_totanx,y=z, color=dep_group)) + geom_point() + 
  geom_smooth(method=lm)
```

```{r}
cor(vs_vcr_social_fltr[vs_vcr_social_fltr$dep_group == 'high',]$z,
          vs_vcr_social_fltr[vs_vcr_social_fltr$dep_group == 'high',]$ch_totanx,
    method='spearman')
```


```{r}
library(ggpubr)

test <- vs_vcr_social_fltr[vs_vcr_social_fltr$dep_group %in% 'low',]

ggscatter(test, x='ch_totanx', y='z',
          add='reg.line',conf.int = TRUE, cor.coef = TRUE, cor.method = 'pearson')
```



## Hypothesis 2


```{r}
cb_vcr_social <- all_sim_vcr_social_rois[all_sim_vcr_social_rois$roi %in% 'region08',]

# Rename subject column name
colnames(cb_vcr_social)[colnames(cb_vcr_social) == 'subj'] <- 'subject_id'

cb_vcr_social_behav <- merge(cb_vcr_social,full_data, by='subject_id')

# Filter for just the kids
cb_vcr_social_behav <- cb_vcr_social_behav[cb_vcr_social_behav$group %in% 'kid',]

# Bin depression in low and high groups
cb_vcr_social_behav <- cb_vcr_social_behav %>% mutate(dep_group = case_when(ch_cdi_total >= 9 ~ 'high',
                                                                            ch_cdi_total < 9 ~ 'low'))


# Filter for relevant variables
cb_vcr_social_fltr <- cb_vcr_social_behav[c('subject_id','z','ch_totanx','ch_cdi_total')]


```

```{r}
anova_mod_cb_sim <- aov(z ~ ch_totanx*ch_cdi_total, data=cb_vcr_social_fltr)
summary(anova_mod_cb_sim)
```


```{r}
lm_vs_sim <- aov(z ~ ch_totanx*ch_cdi_total, data=cb_vcr_social_fltr)
summary(lm_vs_sim)
```




# Age


```{r}
participants_good <- read.csv('../participants_good.tsv', sep = '\t')

# Rename subject column name
colnames(participants_good)[colnames(participants_good) == 'participant_id'] <- 'subject_id'

participants_good
```



```{r}
vs_vcr_social <- all_sim_vcr_social_rois[all_sim_vcr_social_rois$roi %in% 'striatum_ventral',]

# Rename subject column name
colnames(vs_vcr_social)[colnames(vs_vcr_social) == 'subj'] <- 'subject_id'

vs_vcr_social_age <- merge(vs_vcr_social,participants_good, by='subject_id')


# Filter for relevant variables
vs_vcr_social_fltr <- vs_vcr_social_age[c('subject_id','z','age')]

```

```{r}
lm_age <- lm(z ~ age, data=vs_vcr_social_fltr)
summary(lm_age)
```



```{r}
cb_vcr_social <- all_sim_vcr_social_rois[all_sim_vcr_social_rois$roi %in% 'region08',]

# Rename subject column name
colnames(cb_vcr_social)[colnames(cb_vcr_social) == 'subj'] <- 'subject_id'

cb_vcr_social_age <- merge(cb_vcr_social,participants_good, by='subject_id')



# Filter for relevant variables
cb_vcr_social_fltr <- cb_vcr_social_age[c('subject_id','z','age')]


```

```{r}
lm_age <- lm(z ~ age, data=cb_vcr_social_fltr)
summary(lm_age)
```





```{r}

all_sim_vcr_mdoors_rois.ttests <- data.frame(matrix(ncol=7,nrow=0))
all_sim_vcr_social_rois.ttests <- data.frame(matrix(ncol=7,nrow=0))
colnames(all_sim_vcr_mdoors_rois.ttests) <- c('roi','t_stat','p','estimate','CI_l','CI_h','df')
colnames(all_sim_vcr_social_rois.ttests) <- c('roi','t_stat','p','estimate','CI_l','CI_h','df')

row_n = 1
for (roi in hyp_rois) {
  # Filter for ROI data
  roi_data_mdoors <- all_sim_vcr_mdoors_rois[all_sim_vcr_mdoors_rois$roi %in% roi, ]
  roi_data_social <- all_sim_vcr_social_rois[all_sim_vcr_social_rois$roi %in% roi, ]
  
  # Calculate t-test
  temp_ttest_mdoors <- t.test(roi_data_mdoors$r, mu=0)
  temp_ttest_social <- t.test(roi_data_social$r, mu=0)
  
  # Fill in dataframe
  all_sim_vcr_mdoors_rois.ttests[row_n,] <- c(roi,temp_ttest_mdoors$statistic,
                                              temp_ttest_mdoors$p.value,
                                              temp_ttest_mdoors$estimate, 
                                              temp_ttest_mdoors$conf.int[1],
                                              temp_ttest_mdoors$conf.int[2],
                                              temp_ttest_mdoors$parameter[[1]])
  all_sim_vcr_social_rois.ttests[row_n,] <- c(roi,temp_ttest_social$statistic,
                                              temp_ttest_social$p.value,
                                              temp_ttest_social$estimate, 
                                              temp_ttest_social$conf.int[1],
                                              temp_ttest_social$conf.int[2],
                                              temp_ttest_social$parameter[[1]])
      
  # Increase counter for row numbers
      
  row_n = row_n+1
}

all_sim_vcr_mdoors_rois.ttests$p_adjust <- p.adjust(all_sim_vcr_mdoors_rois.ttests$p,
                                                   method='fdr')
all_sim_vcr_social_rois.ttests$p_adjust <- p.adjust(all_sim_vcr_social_rois.ttests$p,
                                                   method='fdr')


```




