---
title: "Social Doors RSA"
author: "Haroon Popal"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    number_sections: true
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 2
    df_print: paged
    css: !expr here::here("./style_srk_behavioral.css")
    knit: (function(inputFile, encoding) { 
      out_dir <- './';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'index.html')) })
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

require("knitr")
opts_knit$set(root.dir = "~/OneDrive - Temple University/olson_lab/projects/social_doors/derivatives/rsa-bw_runs/")
```


```{r}
library(ggplot2)
library(dplyr)
library(reshape2)
library(psych)
library(ggpubr)
library(stringr)
library(kableExtra)
```


# Being correct is being correct
```{r}
rdm_cex = c(c(0,1,1,1,1,1),
            c(1,0,1,1,0,1),
            c(1,1,0,1,1,0),
            c(1,1,1,0,1,1),
            c(1,0,1,1,0,1),
            c(1,1,0,1,1,0))

dim(rdm_cex) <- c(6,6)

conditions = c('Negative','Negative Win','Negative Loss',
               'Positive','Positive Win','Positive Loss')

dimnames(rdm_cex) = list(conditions, conditions)

rdm_cex_melt <- melt(rdm_cex)

ggplot(rdm_cex_melt, aes(x=Var1, y=ordered(Var2, levels = rev(sort(unique(Var2)))), fill=value)) +
  geom_tile(width = 1, color = 'grey') +
  theme_minimal() + 
  scale_fill_distiller(palette = "Oranges", direction = 1) + 
  labs(title = "Domain General Outcome RDM", x = "\nTask Conditions", y = "", fill = 'Dissimilarity') + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", angle = 45, vjust = 0.5),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), plot.background = element_blank())

ggsave('rdm_cex.png')
```

```{r}
# Import data
all_sim_cex <- read.csv(file='crctexc_rdm_similarity.csv', header = TRUE)

# Use "adult as group label
all_sim_cex$group[all_sim_cex$group == 'control'] <- 'adult'
all_sim_cex$group[all_sim_cex$group == 'college'] <- 'adult'

all_sim_cex
```

Divide data by task
```{r}
all_sim_cex_mdoors <- all_sim_cex[all_sim_cex$task %in% 'mdoors', ]
all_sim_cex_social <- all_sim_cex[all_sim_cex$task %in% 'social', ]

```

Filter data by hypothesized ROIs
```{r}
hyp_rois <- c('TPJ_b-social','region08','region02','striatum_ventral','striatum_dorsalp')
hyp_rois_names <- c('TPJ','CB Region 8','CB Region 2','Ventral Striatum','Posterior Dorsal \n Striatum')

all_sim_cex_mdoors_rois <- all_sim_cex_mdoors[all_sim_cex_mdoors$roi %in% hyp_rois, ]
all_sim_cex_social_rois <- all_sim_cex_social[all_sim_cex_social$roi %in% hyp_rois, ]

```




```{r}

all_sim_cex_mdoors_rois.ttests <- data.frame(matrix(ncol=7,nrow=0))
all_sim_cex_social_rois.ttests <- data.frame(matrix(ncol=7,nrow=0))
colnames(all_sim_cex_mdoors_rois.ttests) <- c('roi','t_stat','p','estimate','CI_l','CI_h','df')
colnames(all_sim_cex_social_rois.ttests) <- c('roi','t_stat','p','estimate','CI_l','CI_h','df')

row_n = 1
for (roi in hyp_rois) {
  # Filter for ROI data
  roi_data_mdoors <- all_sim_cex_mdoors_rois[all_sim_cex_mdoors_rois$roi %in% roi, ]
  roi_data_social <- all_sim_cex_social_rois[all_sim_cex_social_rois$roi %in% roi, ]
  
  # Calculate t-test
  temp_ttest_mdoors <- t.test(roi_data_mdoors$r, mu=0)
  temp_ttest_social <- t.test(roi_data_social$r, mu=0)
  
  # Fill in dataframe
  all_sim_cex_mdoors_rois.ttests[row_n,] <- c(roi,temp_ttest_mdoors$statistic,
                                              temp_ttest_mdoors$p.value,
                                              temp_ttest_mdoors$estimate, 
                                              temp_ttest_mdoors$conf.int[1],
                                              temp_ttest_mdoors$conf.int[2],
                                              temp_ttest_mdoors$parameter[[1]])
  all_sim_cex_social_rois.ttests[row_n,] <- c(roi,temp_ttest_social$statistic,
                                              temp_ttest_social$p.value,
                                              temp_ttest_social$estimate, 
                                              temp_ttest_social$conf.int[1],
                                              temp_ttest_social$conf.int[2],
                                              temp_ttest_social$parameter[[1]])
      
  # Increase counter for row numbers
      
  row_n = row_n+1
}

all_sim_cex_mdoors_rois.ttests$p_adjust <- p.adjust(all_sim_cex_mdoors_rois.ttests$p,
                                                   method='fdr')
all_sim_cex_social_rois.ttests$p_adjust <- p.adjust(all_sim_cex_social_rois.ttests$p,
                                                   method='fdr')

```



## Monetary

### ANOVA
```{r}
anova_mod_sim_cor <- aov(r ~ roi, data=all_sim_cex_mdoors_rois)
summary(anova_mod_sim_cor)
```


```{r}
x <- all_sim_cex_mdoors_rois$r
factor <- all_sim_cex_mdoors_rois$roi

mean.sd <- function(x) c(mean = mean(x), sd = sd(x))
simplify2array(tapply(x, factor, mean.sd))
```


## Post-hoc Tests
```{r}
tukey.test <- TukeyHSD(anova_mod_sim_cor)
tukey.test
```


```{r}
stats <- compare_means(r ~ roi, , data = all_sim_cex_mdoors_rois, method = "t.test",
                       p.adjust.method = 'fdr')
stats
```



```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

p <- ggbarplot(all_sim_cex_mdoors_rois, x = 'roi', 
               y = 'r', add = 'mean_se',
               fill=cbPalette[7],
               position = position_dodge(0.8))
p + theme(axis.text.x = element_text(angle =45, vjust = 0.5)) + 
  #geom_signif(comparisons = list(c("region06", "striatum_ventral"),
  #                               c('region06','striatum_dorsalp')),
  #            map_signif_level = TRUE,
  #            annotations = c('***','*'), y_position = c(0.166,0.185), vjust=0.1) + 
  scale_x_discrete(labels=hyp_rois_names) + 
  xlab("Regions of Interests") + ylab("Spearman's rho") + 
  ggtitle("Similarity to Domain Neutral Outcome in Monetary Task") 

ggsave('rsa_cex_mdoors.png')

```



### One sample t-tests
#### Right Crus I
```{r}
roi_c1_r <- all_sim_cex_mdoors[all_sim_cex_mdoors$roi == 'region08',]$r
roi_c1_z <- fisherz(roi_c1_r)
t.test(roi_c1_z, mu = 0)
```


#### Bilateral Ventrial Striatum
```{r}
roi_VS_b <- all_sim_cex_mdoors[all_sim_cex_mdoors$roi == 'striatum_ventral',]$r
roi_VS_z <- fisherz(roi_VS_b)
t.test(roi_VS_z, mu = 0)
```



## Social

### ANOVA
```{r}
anova_mod_sim_cex <- aov(r ~ roi, data=all_sim_cex_social_rois)
summary(anova_mod_sim_cex)
```

```{r}
x <- all_sim_cex_social_rois$r
factor <- all_sim_cex_social_rois$roi

mean.sd <- function(x) c(mean = mean(x), sd = sd(x))
simplify2array(tapply(x, factor, mean.sd))
```


## Post-hoc Tests
```{r}
tukey.test <- TukeyHSD(anova_mod_sim_cex)
tukey.test
```


```{r}
stats <- compare_means(r ~ roi, , data = all_sim_cex_social_rois, method = "t.test",
                       p.adjust.method = 'fdr')
stats
```


```{r}
p <- ggbarplot(all_sim_cex_social_rois, x = 'roi', 
               y = 'r', add = 'mean_se',
               fill=cbPalette[7],
               position = position_dodge(0.8))
p + theme(axis.text.x = element_text(angle =45, vjust = 0.5)) + 
  #geom_signif(comparisons = list(c("region08", "striatum_ventral")),
  #            map_signif_level = TRUE,
  #            annotations = c('*'), y_position = c(0.235), vjust=0.1) +  
  scale_x_discrete(labels=hyp_rois_names) + 
  xlab("Regions of Interests") + ylab("Spearman's rho") + 
  ggtitle("Similarity to Domain Neutral Outcome in Social Task") 

ggsave('rsa_cex_social.png')

```



### One sample t-tests
#### Right Crus I
```{r}
roi_c1_r <- all_sim_cex_social[all_sim_cex_social$roi == 'region08',]$r
roi_c1_z <- fisherz(roi_c1_r)
t.test(roi_c1_z, mu = 0)
```


#### Bilateral Ventrial Striatum
```{r}
roi_VS_b <- all_sim_cex_social[all_sim_cex_social$roi == 'striatum_ventral',]$r
roi_VS_z <- fisherz(roi_VS_b)
t.test(roi_VS_z, mu = 0)
```











# Positive win is different from negative win
```{r}
all_sim_vcr <- read.csv(file='corrval_rdm_similarity.csv', header = TRUE)
all_sim_vcr
```


```{r}
# Use "adult as group label
all_sim_vcr$group[all_sim_vcr$group == 'control'] <- 'adult'
all_sim_vcr$group[all_sim_vcr$group == 'college'] <- 'adult'
```



Divide data by task
```{r}
all_sim_vcr_mdoors <- all_sim_vcr[all_sim_vcr$task %in% 'mdoors', ]
all_sim_vcr_social <- all_sim_vcr[all_sim_vcr$task %in% 'social', ]

```

Filter data by hypothesized ROIs
```{r}
hyp_rois <- c('striatum_ventral','striatum_dorsalp','region08','region02','TPJ_b-social')

all_sim_vcr_mdoors_rois <- all_sim_vcr_mdoors[all_sim_vcr_mdoors$roi %in% hyp_rois, ]
all_sim_vcr_social_rois <- all_sim_vcr_social[all_sim_vcr_social$roi %in% hyp_rois, ]
#all_sim_vcr_social_rois$roi <- factor(all_sim_vcr_social_rois$roi, levels=hyp_rois)

```


Fischer r to z transform
```{r}
all_sim_vcr_mdoors_rois$z <- fisherz(all_sim_vcr_mdoors_rois$r)
all_sim_vcr_social_rois$z <- fisherz(all_sim_vcr_social_rois$r)

```




```{r}

all_sim_vcr_mdoors_rois.ttests <- data.frame(matrix(ncol=7,nrow=0))
all_sim_vcr_social_rois.ttests <- data.frame(matrix(ncol=7,nrow=0))
colnames(all_sim_vcr_mdoors_rois.ttests) <- c('roi','t_stat','p','estimate','CI_l','CI_h','df')
colnames(all_sim_vcr_social_rois.ttests) <- c('roi','t_stat','p','estimate','CI_l','CI_h','df')

row_n = 1
for (roi in hyp_rois) {
  # Filter for ROI data
  roi_data_mdoors <- all_sim_vcr_mdoors_rois[all_sim_vcr_mdoors_rois$roi %in% roi, ]
  roi_data_social <- all_sim_vcr_social_rois[all_sim_vcr_social_rois$roi %in% roi, ]
  
  # Calculate t-test
  temp_ttest_mdoors <- t.test(roi_data_mdoors$r, mu=0)
  temp_ttest_social <- t.test(roi_data_social$r, mu=0)
  
  # Fill in dataframe
  all_sim_vcr_mdoors_rois.ttests[row_n,] <- c(roi,temp_ttest_mdoors$statistic,
                                              temp_ttest_mdoors$p.value,
                                              temp_ttest_mdoors$estimate, 
                                              temp_ttest_mdoors$conf.int[1],
                                              temp_ttest_mdoors$conf.int[2],
                                              temp_ttest_mdoors$parameter[[1]])
  all_sim_vcr_social_rois.ttests[row_n,] <- c(roi,temp_ttest_social$statistic,
                                              temp_ttest_social$p.value,
                                              temp_ttest_social$estimate, 
                                              temp_ttest_social$conf.int[1],
                                              temp_ttest_social$conf.int[2],
                                              temp_ttest_social$parameter[[1]])
      
  # Increase counter for row numbers
      
  row_n = row_n+1
}

all_sim_vcr_mdoors_rois.ttests$p_adjust <- p.adjust(all_sim_vcr_mdoors_rois.ttests$p,
                                                   method='fdr')
all_sim_vcr_social_rois.ttests$p_adjust <- p.adjust(all_sim_vcr_social_rois.ttests$p,
                                                   method='fdr')

```


## Monetary

### ANOVA
```{r}
anova_mod_sim_vcr <- aov(r ~ roi, data=all_sim_vcr_mdoors_rois)
summary(anova_mod_sim_vcr)
```



```{r}
x <- all_sim_vcr_mdoors_rois$r
factor <- all_sim_vcr_mdoors_rois$roi

mean.sd <- function(x) c(mean = mean(x), sd = sd(x))
simplify2array(tapply(x, factor, mean.sd))
```


## Post-hoc Tests
```{r}
tukey.test <- TukeyHSD(anova_mod_sim_vcr)
tukey.test
```

```{r}
stats <- compare_means(r ~ roi, , data = all_sim_vcr_mdoors_rois, method = "t.test",
                       p.adjust.method = 'fdr')
stats
```

```{r}
P_adjust <- all_sim_vcr_mdoors_rois.ttests$p_adjust
Sig_adjust = ifelse(P_adjust < 0.005, "***", ifelse(P_adjust < 0.01, "**", 
                                             ifelse(P_adjust < 0.05, "*", "")))

p <- ggbarplot(all_sim_vcr_mdoors_rois, x = 'roi', 
               y = 'r', add = 'mean_se',
               fill=cbPalette[6],
               position = position_dodge(0.8))
p + theme(axis.text.x = element_text(angle =45, vjust = 0.5)) + 
  geom_signif(comparisons = list(c("region08", "striatum_ventral")),
              map_signif_level = TRUE,
              annotations = c('*'), y_position = c(0.075,0.095), vjust=0.1) + 
  scale_x_discrete(labels=c('TPJ','Region 8','Region 2','Ventral Striatum',
                            'Dorsal Posterior \n Striatum')) + 
  xlab("Regions of Interests") + ylab("Spearman's rho") + 
  ggtitle("Positive and Negative Win Similarity in Monetary Task") 

ggsave('rsa_vcr_mdoors.png')

```



### One sample t-tests
#### Right Crus I
```{r}
roi_c1_r <- all_sim_vcr_mdoors[all_sim_vcr_mdoors$roi == 'region08',]$r
roi_c1_z <- fisherz(roi_c1_r)
t.test(roi_c1_z, mu = 0)
```


#### Bilateral Ventrial Striatum
```{r}
roi_VS_b <- all_sim_vcr_mdoors[all_sim_vcr_mdoors$roi == 'striatum_ventral',]$r
roi_VS_z <- fisherz(roi_VS_b)
t.test(roi_VS_z, mu = 0)
```



## Social

### ANOVA
```{r}
anova_mod_sim_vcr <- aov(r ~ roi, data=all_sim_vcr_social_rois)
summary(anova_mod_sim_vcr)
```

```{r}
x <- all_sim_vcr_social_rois$r
factor <- all_sim_vcr_social_rois$roi

mean.sd <- function(x) c(mean = mean(x), sd = sd(x))
simplify2array(tapply(x, factor, mean.sd))
```

```{r}
tapply(x, factor, sd)
```




## Post-hoc Tests
```{r}
tukey.test <- TukeyHSD(anova_mod_sim_vcr)
tukey.test
```



```{r}
stats <- compare_means(r ~ roi, , data = all_sim_vcr_social_rois, method = "t.test",
                       p.adjust.method = 'fdr')
stats
```




```{r}

P_adjust <- all_sim_vcr_social_rois.ttests$p_adjust
Sig_adjust = ifelse(P_adjust < 0.005, "***", ifelse(P_adjust < 0.01, "**", 
                                             ifelse(P_adjust < 0.05, "*", "")))

p <- ggbarplot(all_sim_vcr_social_rois, x = 'roi', 
               y = 'r', add = 'mean_se',
               fill=cbPalette[6],
               position = position_dodge(0.8))
p + theme(axis.text.x = element_text(angle =45, vjust = 0.5)) + 
  geom_signif(comparisons = list(c("region08", "striatum_ventral"),
                                 c('region08','striatum_dorsalp'),
                                 c('region08','region02'),
                                 c('region08','TPJ_b-social')),
              map_signif_level = TRUE,
              annotations = c('***','***','*','*'), 
              y_position = c(0.155,0.18,0.13,0.205), vjust=0.1) + 
  scale_x_discrete(labels=c('TPJ','Region 8','Region 2','Ventral Striatum',
                            'Dorsal Posterior \n Striatum')) + 
  xlab("Regions of Interests") + ylab("Spearman's rho") + 
  ggtitle("Positive and Negative Win Similarity in Social Task")
ggsave('rsa_vcr_social.png')

```



### One sample t-tests
#### Right Crus I
```{r}
roi_c1_r <- all_sim_vcr_social[all_sim_vcr_social$roi == 'region08',]$r
roi_c1_z <- fisherz(roi_c1_r)
t.test(roi_c1_z, mu = 0)
```


#### Bilateral Ventrial Striatum
```{r}
roi_VS_b <- all_sim_vcr_social[all_sim_vcr_social$roi == 'striatum_ventral',]$r
roi_VS_z <- fisherz(roi_VS_b)
t.test(roi_VS_z, mu = 0)
```


## Combine one-sample t-test data
```{r}
all_sim_cex_mdoors_rois.ttests$source <- 'cex_mdoors'
all_sim_cex_social_rois.ttests$source <- 'cex_social'
all_sim_vcr_mdoors_rois.ttests$source <- 'vcr_mdoors'
all_sim_vcr_social_rois.ttests$source <- 'vcr_social'

one_sample_ttests <- rbind(all_sim_cex_mdoors_rois.ttests, all_sim_cex_social_rois.ttests,
                     all_sim_vcr_mdoors_rois.ttests, all_sim_vcr_social_rois.ttests)

```

Fix up dataframe for pretty table
```{r}
# Sort dataframe
one_sample_table <- one_sample_ttests[order(one_sample_ttests$source, one_sample_ttests$roi), ]

# Rename ROI names
rep_str = c('region02'='CB Region 2','region08'='CB Region 8',
            'striatum_dorsalp'='Posterior Dorsal Striatum','striatum_ventral'='Ventral Striatum',
            'TPJ_b-social'='TPJ')
one_sample_table$roi <- str_replace_all(one_sample_table$roi, rep_str)

# Turn columns numeric
one_sample_table$t_stat <- as.numeric(one_sample_table$t_stat)
one_sample_table$estimate <- as.numeric(one_sample_table$estimate)
one_sample_table$CI_l <- as.numeric(one_sample_table$CI_l)
one_sample_table$CI_h <- as.numeric(one_sample_table$CI_h)
one_sample_table$p_adjust <- as.numeric(one_sample_table$p_adjust)

# Round numbers
one_sample_table$t_stat <- round(one_sample_table$t_stat,2)
one_sample_table$estimate <- round(one_sample_table$estimate,2)
one_sample_table$CI_l <- round(one_sample_table$CI_l,2)
one_sample_table$CI_h <- round(one_sample_table$CI_h,2)
one_sample_table$p_adjust <- round(one_sample_table$p_adjust,3)

# Combine confidence inverval ranges
one_sample_table$CI <- paste('[', as.character(one_sample_table$CI_l),
                              ', ', as.character(one_sample_table$CI_h), ']')

# Reorder columns
one_sample_table <- one_sample_table[, c("roi", "estimate", "df", "t_stat",
                                           "p_adjust", "CI")]

colnames(one_sample_table) <- c('ROI','Mean','df','t-statistic','p','CI')

```

```{r}
one_sample_table %>%
  kbl(caption = "RSA results for a full and partial similarity analysis") %>%
  kable_classic(full_width = F, html_font = "Times New Roman") %>%
  save_kable("one_sample_ttests.html")


one_sample_table %>%
  kbl(caption = "RSA results for a full and partial similarity analysis") %>%
  kable_classic(full_width = F, html_font = "Times New Roman")
```



---

# Behavioral Analysis
Research Question: Does greater similarity for positive and negative wins relate to anxiety and depression?

Hypothesis 1: Greater similarity between positive and negative wins in the ventral striatum will be related to greater anxiety and less depression
(Quarmley replication)

Hypothesis 2: Greater similarity between positive and negative wins in the cerebellum ...

```{r}
library(readxl)
library(dplyr)
```


```{r}
full_data <- read.csv('../../misc/aggregate_paper_data_SPSS_020419.csv')

full_data$Subject <- gsub('s', 'sub-', full_data$Subject)

# Rename subject column name
colnames(full_data)[colnames(full_data) == 'Subject'] <- 'subject_id'

full_data
```


## Hypothesis 1 testing

```{r}
vs_vcr_social <- all_sim_vcr_social_rois[all_sim_vcr_social_rois$roi %in% 'region08',]

# Rename subject column name
colnames(vs_vcr_social)[colnames(vs_vcr_social) == 'subj'] <- 'subject_id'

vs_vcr_social_behav <- merge(vs_vcr_social,full_data, by='subject_id')

# Filter for just the kids
vs_vcr_social_behav <- vs_vcr_social_behav[vs_vcr_social_behav$group %in% 'kid',]

# Bin depression in low and high groups
vs_vcr_social_behav <- vs_vcr_social_behav %>% mutate(dep_group = case_when(ch_cdi_total >= 9 ~ 'high',
                                                                            ch_cdi_total < 9 ~ 'low'))

# Filter for relevant variables
vs_vcr_social_fltr <- vs_vcr_social_behav[c('subject_id','z','ch_totanx','dep_group')]


```

```{r}
anova_mod_vs_sim <- aov(z ~ ch_totanx*dep_group, data=vs_vcr_social_fltr)
summary(anova_mod_vs_sim)
```


```{r}
lm_vs_sim <- aov(z ~ ch_totanx, data=vs_vcr_social_fltr)
summary(lm_vs_sim)
```


```{r}
ggplot(data=vs_vcr_social_fltr,aes(x=ch_totanx,y=z, color=dep_group)) + geom_point() + 
  geom_smooth(method=lm)
```

```{r}
cor(vs_vcr_social_fltr[vs_vcr_social_fltr$dep_group == 'high',]$z,
          vs_vcr_social_fltr[vs_vcr_social_fltr$dep_group == 'high',]$ch_totanx,
    method='spearman')
```


```{r}
library(ggpubr)

test <- vs_vcr_social_fltr[vs_vcr_social_fltr$dep_group %in% 'low',]

ggscatter(test, x='ch_totanx', y='z',
          add='reg.line',conf.int = TRUE, cor.coef = TRUE, cor.method = 'pearson')
```



## Hypothesis 2


```{r}
cb_vcr_social <- all_sim_vcr_social_rois[all_sim_vcr_social_rois$roi %in% 'region08',]

# Rename subject column name
colnames(cb_vcr_social)[colnames(cb_vcr_social) == 'subj'] <- 'subject_id'

cb_vcr_social_behav <- merge(cb_vcr_social,full_data, by='subject_id')

# Filter for just the kids
cb_vcr_social_behav <- cb_vcr_social_behav[cb_vcr_social_behav$group %in% 'kid',]

# Bin depression in low and high groups
cb_vcr_social_behav <- cb_vcr_social_behav %>% mutate(dep_group = case_when(ch_cdi_total >= 9 ~ 'high',
                                                                            ch_cdi_total < 9 ~ 'low'))


# Filter for relevant variables
cb_vcr_social_fltr <- cb_vcr_social_behav[c('subject_id','z','ch_totanx','ch_cdi_total')]


```

```{r}
anova_mod_cb_sim <- aov(z ~ ch_totanx*dep_group, data=cb_vcr_social_fltr)
summary(anova_mod_cb_sim)
```


```{r}
lm_vs_sim <- aov(z ~ ch_totanx*ch_cdi_total, data=cb_vcr_social_fltr)
summary(lm_vs_sim)
```




# Age


```{r}
participants_good <- read.csv('../participants_good.tsv', sep = '\t')

# Rename subject column name
colnames(participants_good)[colnames(participants_good) == 'participant_id'] <- 'subject_id'

participants_good
```



```{r}
vs_vcr_social <- all_sim_vcr_social_rois[all_sim_vcr_social_rois$roi %in% 'striatum_ventral',]

# Rename subject column name
colnames(vs_vcr_social)[colnames(vs_vcr_social) == 'subj'] <- 'subject_id'

vs_vcr_social_age <- merge(vs_vcr_social,participants_good, by='subject_id')


# Filter for relevant variables
vs_vcr_social_fltr <- vs_vcr_social_age[c('subject_id','z','age')]

```

```{r}
lm_age <- lm(z ~ age, data=vs_vcr_social_fltr)
summary(lm_age)
```



```{r}
cb_vcr_social <- all_sim_vcr_social_rois[all_sim_vcr_social_rois$roi %in% 'region08',]

# Rename subject column name
colnames(cb_vcr_social)[colnames(cb_vcr_social) == 'subj'] <- 'subject_id'

cb_vcr_social_age <- merge(cb_vcr_social,participants_good, by='subject_id')



# Filter for relevant variables
cb_vcr_social_fltr <- cb_vcr_social_age[c('subject_id','z','age')]


```

```{r}
lm_age <- lm(z ~ age, data=cb_vcr_social_fltr)
summary(lm_age)
```





```{r}

all_sim_vcr_mdoors_rois.ttests <- data.frame(matrix(ncol=7,nrow=0))
all_sim_vcr_social_rois.ttests <- data.frame(matrix(ncol=7,nrow=0))
colnames(all_sim_vcr_mdoors_rois.ttests) <- c('roi','t_stat','p','estimate','CI_l','CI_h','df')
colnames(all_sim_vcr_social_rois.ttests) <- c('roi','t_stat','p','estimate','CI_l','CI_h','df')

row_n = 1
for (roi in hyp_rois) {
  # Filter for ROI data
  roi_data_mdoors <- all_sim_vcr_mdoors_rois[all_sim_vcr_mdoors_rois$roi %in% roi, ]
  roi_data_social <- all_sim_vcr_social_rois[all_sim_vcr_social_rois$roi %in% roi, ]
  
  # Calculate t-test
  temp_ttest_mdoors <- t.test(roi_data_mdoors$r, mu=0)
  temp_ttest_social <- t.test(roi_data_social$r, mu=0)
  
  # Fill in dataframe
  all_sim_vcr_mdoors_rois.ttests[row_n,] <- c(roi,temp_ttest_mdoors$statistic,
                                              temp_ttest_mdoors$p.value,
                                              temp_ttest_mdoors$estimate, 
                                              temp_ttest_mdoors$conf.int[1],
                                              temp_ttest_mdoors$conf.int[2],
                                              temp_ttest_mdoors$parameter[[1]])
  all_sim_vcr_social_rois.ttests[row_n,] <- c(roi,temp_ttest_social$statistic,
                                              temp_ttest_social$p.value,
                                              temp_ttest_social$estimate, 
                                              temp_ttest_social$conf.int[1],
                                              temp_ttest_social$conf.int[2],
                                              temp_ttest_social$parameter[[1]])
      
  # Increase counter for row numbers
      
  row_n = row_n+1
}

all_sim_vcr_mdoors_rois.ttests$p_adjust <- p.adjust(all_sim_vcr_mdoors_rois.ttests$p,
                                                   method='fdr')
all_sim_vcr_social_rois.ttests$p_adjust <- p.adjust(all_sim_vcr_social_rois.ttests$p,
                                                   method='fdr')


```




