---
title: "Social Doors RSA"
author: "Haroon Popal"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    number_sections: true
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 2
    df_print: paged
    css: !expr here::here("./style_srk_behavioral.css")
    knit: (function(inputFile, encoding) { 
      out_dir <- './';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'index.html')) })
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

require("knitr")
opts_knit$set(root.dir = "~/OneDrive - Temple University/olson_lab/projects/social_doors/derivatives/rsa/")
```


```{r}
library(ggplot2)
library(dplyr)
library(reshape2)
```






# Valence
```{r}
rdm_val = c(c(0,0,0,1,1,1),
            c(0,0,0,1,1,1),
            c(0,0,0,1,1,1),
            c(1,1,1,0,0,0),
            c(1,1,1,0,0,0),
            c(1,1,1,0,0,0))

dim(rdm_val) <- c(6,6)

conditions = c('Negative','Negative Win','Negative Loss',
               'Positive','Positive Win','Positive Loss')

dimnames(rdm_val) = list(conditions, conditions)

rdm_val_melt <- melt(rdm_val)

ggplot(rdm_val_melt, aes(x=Var1, y=ordered(Var2, levels = rev(sort(unique(Var2)))), fill=value)) +
  geom_tile(width = 1, color='grey') +
  scale_fill_distiller(direction = 1) +
  labs(title = "Valence RDM", x = "\nTask Conditions", y = "", fill = 'Dissimilarity') + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", angle = 45, vjust = 0.5),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), plot.background = element_blank())

ggsave('rdm_val.png')
```


```{r}
all_sim_val <- read.csv(file='valence_rdm_similarity.csv', header = TRUE)
all_sim_val

# Use "adult as group label
all_sim_val$group[all_sim_val$group == 'control'] <- 'adult'
all_sim_val$group[all_sim_val$group == 'college'] <- 'adult'
```


## Filter for group and task
```{r}
sim_val_adole <- all_sim_val[(all_sim_val$group == 'kid'), ]

# Filter for ROIs
sim_val_adole_roi <- sim_val_adole[(sim_val_adole$roi == 'VS_l-rlearn') | (sim_val_adole$roi == 'C1_r-social') | (sim_val_adole$roi == 'LIX_r-rlearn'), ]

# Filter for only the social task
sim_val_adole_roi_social <- sim_val_adole_roi[(sim_val_adole_roi$task == 'social'), ]


```

## ANOVA
```{r}
anova_mod_sim_val <- aov(r ~ roi, data=sim_val_adole_roi_social)
summary(anova_mod_sim_val)
```

## Post-hoc Tests
```{r}
tukey.test <- TukeyHSD(anova_mod_sim_val)
tukey.test
```


```{r}
ggplot(sim_val_adole_roi_social, aes(x=roi, y=r)) + 
  #stat_summary(fun.data=mean_sdl, geom='bar', position=position_dodge()) + 
  geom_bar(stat = 'summary', position=position_dodge()) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=90))
```

## One sample t-tests
### Right Crus I
```{r}
roi_c1_r <- sim_val_adole_roi_social[sim_val_adole_roi_social$roi == 'C1_r-social',]$r
roi_c1_z <- fisherz(roi_c1_r)
t.test(roi_c1_z, mu = 0)
```

### Right Lobule IX
```{r}
roi_LIX_r <- sim_val_adole_roi_social[sim_val_adole_roi_social$roi == 'LIX_r-rlearn',]$r
roi_LIX_z <- fisherz(roi_LIX_r)
t.test(roi_LIX_z, mu = 0)
```

### Left Ventrial Striatum
```{r}
roi_VS_r <- sim_val_adole_roi_social[sim_val_adole_roi_social$roi == 'VS_l-rlearn',]$r
roi_VS_z <- fisherz(roi_VS_r)
t.test(roi_VS_z, mu = 0)
```



# Being correct is being correct
```{r}
rdm_cor = c(c(0,0,0,0,0,0),
            c(0,0,1,0,0,1),
            c(0,1,0,0,1,0),
            c(0,0,0,0,0,0),
            c(0,0,1,0,0,1),
            c(0,1,0,0,1,0))

dim(rdm_cor) <- c(6,6)

conditions = c('Negative','Negative Win','Negative Loss',
               'Positive','Positive Win','Positive Loss')

dimnames(rdm_cor) = list(conditions, conditions)

rdm_cor_melt <- melt(rdm_cor)

ggplot(rdm_cor_melt, aes(x=Var1, y=ordered(Var2, levels = rev(sort(unique(Var2)))), fill=value)) +
  geom_tile(width = 1, color = 'grey') +
  theme_minimal() + 
  scale_fill_distiller(direction = 1) + 
  labs(title = "Domain General Correct RDM", x = "\nTask Conditions", y = "") + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", angle = 45, vjust = 0.5),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), plot.background = element_blank())

ggsave('rdm_cor.png')
```

```{r}
# Import data
all_sim_cor <- read.csv(file='correct_rdm_similarity.csv', header = TRUE)

# Use "adult as group label
all_sim_cor$group[all_sim_cor$group == 'control'] <- 'adult'
all_sim_cor$group[all_sim_cor$group == 'college'] <- 'adult'

head(all_sim_cor)
```

# Filter for group and relevant ROIs
## Filter for group 
```{r}
# Filter for just adolescents
sim_cor_adole <- all_sim_cor[(all_sim_cor$group == 'kid'), ]

# Filter for ROIs
sim_cor_adole_roi <- sim_cor_adole[(sim_cor_adole$roi == 'VS_l-rlearn') | (sim_cor_adole$roi == 'C1_r-social') | (sim_cor_adole$roi == 'LIX_r-rlearn'), ]

# Filter for only the social task
sim_cor_adole_roi_social <- sim_cor_adole_roi[(sim_cor_adole_roi$task == 'social'), ]

```

## ANOVA
Correlation to model RDM predicted by region of interest
```{r}
anova_mod_sim_cor <- aov(r ~ roi, data=sim_cor_adole_roi_social)
summary(anova_mod_sim_cor)
```


## Post-hoc Test
```{r}
tukey.test <- TukeyHSD(anova_mod_sim_cor)
tukey.test
```

## Visualization
```{r}
ggplot(sim_cor_adole_roi_social, aes(x=roi, y=r)) + 
  #stat_summary(fun.data=mean_sdl, geom='bar', position=position_dodge()) + 
  geom_bar(stat = 'summary', position=position_dodge()) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=90))
```


## One sample t-tests
### Right Crus I
```{r}
roi_c1_r <- sim_cor_adole_roi_social[sim_cor_adole_roi_social$roi == 'C1_r-social',]$r
roi_c1_z <- fisherz(roi_c1_r)
t.test(roi_c1_z, mu = 0)
```

### Right Lobule IX
```{r}
roi_LIX_r <- sim_cor_adole_roi_social[sim_cor_adole_roi_social$roi == 'LIX_r-rlearn',]$r
roi_LIX_z <- fisherz(roi_LIX_r)
t.test(roi_LIX_z, mu = 0)
```

### Left Ventrial Striatum
```{r}
roi_VS_r <- sim_cor_adole_roi_social[sim_cor_adole_roi_social$roi == 'VS_l-rlearn',]$r
roi_VS_z <- fisherz(roi_VS_r)
t.test(roi_VS_z, mu = 0)
```










# Positive win is different from negative win
```{r}
all_sim_vcr <- read.csv(file='corrval_rdm_similarity.csv', header = TRUE)
all_sim_vcr
```


```{r}
# Use "adult as group label
all_sim_vcr$group[all_sim_vcr$group == 'control'] <- 'adult'
all_sim_vcr$group[all_sim_vcr$group == 'college'] <- 'adult'
```



## Filter for group and task
```{r}
sim_vcr_adole <- all_sim_vcr[(all_sim_vcr$group == 'kid'), ]
```


## Filter for ROIs
```{r}
sim_vcr_adole_roi <- sim_vcr_adole[(sim_vcr_adole$roi == 'VS_l-rlearn') | (sim_vcr_adole$roi == 'C1_r-social') | (sim_vcr_adole$roi == 'LIX_r-rlearn'), ]

```

## ANOVA
```{r}
anova_mod_sim_vcr <- aov(r ~ task*roi, data=sim_vcr_adole_roi)
summary(anova_mod_sim_vcr)
```


```{r}
tukey.test <- TukeyHSD(anova_mod_sim_cor)
tukey.test
```


```{r}
ggplot(sim_vcr_adole_roi, aes(x=roi, y=r, fill=task)) + 
  #stat_summary(fun.data=mean_sdl, geom='bar', position=position_dodge()) + 
  geom_bar(stat = 'summary', position=position_dodge()) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=90))
```









# Valence
```{r}
all_sim_val <- read.csv(file='valence_rdm_similarity.csv', header = TRUE)
all_sim_val
```


```{r}
# Use "adult as group label
all_sim_val$group[all_sim_val$group == 'control'] <- 'adult'
all_sim_val$group[all_sim_val$group == 'college'] <- 'adult'
```



## Filter for group and task
```{r}
sim_val_adole <- all_sim_val[(all_sim_val$group == 'kid'), ]
```


## Filter for ROIs
```{r}
sim_val_adole_roi <- sim_val_adole[(sim_val_adole$roi == 'VS_l-rlearn') | (sim_val_adole$roi == 'C1_r-social') | (sim_val_adole$roi == 'LIX_r-rlearn'), ]

```

## ANOVA
```{r}
anova_mod_sim_val <- aov(r ~ task*roi, data=sim_val_adole_roi)
summary(anova_mod_sim_vcr)
```


```{r}
tukey.test <- TukeyHSD(anova_mod_sim_val)
tukey.test
```


```{r}
ggplot(sim_val_adole_roi, aes(x=roi, y=r, fill=task)) + 
  #stat_summary(fun.data=mean_sdl, geom='bar', position=position_dodge()) + 
  geom_bar(stat = 'summary', position=position_dodge()) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=90))
```




































## Filter for ROIs
```{r}
adole_sim_win_roi <- adole_sim_win[(adole_sim_win$roi == 'VS_l-rlearn') | (adole_sim_win$roi == 'C1_r-rlearn') | (adole_sim_win$roi == 'C1_r-social'), ]

```



```{r}
ggplot(adole_sim_win_roi, aes(x=roi, y=r, fill=task)) + 
  #stat_summary(fun.data=mean_sdl, geom='bar', position=position_dodge()) + 
  geom_bar(stat = 'summary', position=position_dodge()) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=90))
```



# ROI to ROI correlation
```{r}
C1_r_social_sim <- read.csv(file='roi_C1_r-social_similarity.csv', header = TRUE)
LIX_r_rlearn_sim <- read.csv(file='roi_LIX_r-rlearn_similarity.csv', header = TRUE)
C1_r_rlearn_sim <- read.csv(file='roi_C1_r-rlearn_similarity.csv', header = TRUE)
C1_r_rlearn_sim
```

```{r}
# Use "adult as group label
C1_r_social_sim$group[C1_r_social_sim$group == 'control'] <- 'adult'
C1_r_social_sim$group[C1_r_social_sim$group == 'college'] <- 'adult'

LIX_r_rlearn_sim$group[LIX_r_rlearn_sim$group == 'control'] <- 'adult'
LIX_r_rlearn_sim$group[LIX_r_rlearn_sim$group == 'college'] <- 'adult'

C1_r_rlearn_sim$group[C1_r_rlearn_sim$group == 'control'] <- 'adult'
C1_r_rlearn_sim$group[C1_r_rlearn_sim$group == 'college'] <- 'adult'
```



Combine data
```{r}
roi_roi_sim <- data.frame(colnames=c('subj','group','task','target','roi','r'))
C1_r_social_sim$target <- 'C1_r-social'
#C1_r_rlearn_sim$target <- 'C1_r-rlearn'
LIX_r_rlearn_sim$target <- 'LIX_r-rlearn'

roi_roi_sim <- rbind(C1_r_social_sim, LIX_r_rlearn_sim)
```

Remove autocorrelations
```{r}
roi_roi_sim <- roi_roi_sim[(roi_roi_sim$r != 1), ]

```

## Filter for group
```{r}
roi_roi_sim_social <- roi_roi_sim[roi_roi_sim$group == 'kid', ]
```

## Filter for ROIs
```{r}
roi_roi_sim_social_roi <- roi_roi_sim_social[(roi_roi_sim_social$roi == 'VS_l-rlearn') | (roi_roi_sim_social$roi == 'TPJ_l-social'), ]

```

```{r}
roi_roi_sim_social_roi <- roi_roi_sim_social_roi[complete.cases(roi_roi_sim_social_roi),]
```


## ANOVA
```{r}
anova_mod_roi_sim <- aov(r ~ task*target*roi, data=roi_roi_sim_social_roi)
summary(anova_mod_roi_sim)
```


```{r}
tukey.test <- TukeyHSD(anova_mod_roi_sim)
tukey.test
```


```{r}
ggplot(roi_roi_sim_social_roi, aes(x=roi, y=r, fill=target, alpha=task)) + 
  #stat_summary(fun.data=mean_sdl, geom='bar', position=position_dodge()) + 
  geom_bar(stat = 'summary', position=position_dodge()) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=90))
```






# Connectivity differences between groups
Remove autocorrelations
```{r}
C1_r_social_sim <- C1_r_social_sim[(C1_r_social_sim$r != 1), ]
LIX_r_rlearn_sim <- LIX_r_rlearn_sim[(LIX_r_rlearn_sim$r != 1), ]

```

## Filter for task
```{r}
C1_r_social_sim_social <- C1_r_social_sim[C1_r_social_sim$task == 'social', ]
LIX_r_rlearn_sim_social <- LIX_r_rlearn_sim[LIX_r_rlearn_sim$task == 'social', ]
```


```{r}
C1_r_social_sim_social <- C1_r_social_sim_social[complete.cases(C1_r_social_sim_social),]
LIX_r_rlearn_sim_social <- LIX_r_rlearn_sim_social[complete.cases(LIX_r_rlearn_sim_social),]
```


## ANOVA
```{r}
anova_mod_roi_sim <- aov(r ~ group*roi, data=C1_r_social_sim_social)
summary(anova_mod_roi_sim)
```


```{r}
ggplot(C1_r_social_sim_social, aes(x=roi, y=r, fill=group)) + 
  #stat_summary(fun.data=mean_sdl, geom='bar', position=position_dodge()) + 
  geom_bar(stat = 'summary', position=position_dodge()) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=90))
```

```{r}
anova_mod_roi_sim <- aov(r ~ group*roi, data=LIX_r_rlearn_sim_social)
summary(anova_mod_roi_sim)
```

```{r}
ggplot(LIX_r_rlearn_sim_social, aes(x=roi, y=r, fill=group)) + 
  #stat_summary(fun.data=mean_sdl, geom='bar', position=position_dodge()) + 
  geom_bar(stat = 'summary', position=position_dodge()) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=90))
```






```{r}
# Use "adult as group label
C1_r_social_sim$group[C1_r_social_sim$group == 'control'] <- 'adult'
C1_r_social_sim$group[C1_r_social_sim$group == 'college'] <- 'adult'

LIX_r_rlearn_sim$group[LIX_r_rlearn_sim$group == 'control'] <- 'adult'
LIX_r_rlearn_sim$group[LIX_r_rlearn_sim$group == 'college'] <- 'adult'

C1_r_rlearn_sim$group[C1_r_rlearn_sim$group == 'control'] <- 'adult'
C1_r_rlearn_sim$group[C1_r_rlearn_sim$group == 'college'] <- 'adult'
```


Filter by group and task
```{r}
C1_r_social_sim_adole_social <- C1_r_social_sim[(C1_r_social_sim$group == 'kid') & (C1_r_social_sim$task == 'social'), ]
C1_r_rlearn_sim_adole_social <- C1_r_rlearn_sim[(C1_r_rlearn_sim$group == 'kid') & (C1_r_rlearn_sim$task == 'social'), ]
LIX_r_rlearn_sim_adole_social <- LIX_r_rlearn_sim[(LIX_r_rlearn_sim$group == 'kid') & (LIX_r_rlearn_sim$task == 'social'), ]
```



```{r}
C1_r_social_sim_adole_social[complete.cases(C1_r_social_sim_adole_social), ]
C1_r_social_sim_adole_social %>%
  group_by(roi) %>%
  summarise_at(vars(r), list(name = mean))
```

```{r}
C1_r_rlearn_sim_adole_social<- C1_r_rlearn_sim_adole_social[complete.cases(C1_r_rlearn_sim_adole_social), ]
C1_r_rlearn_sim_adole_social %>%
  group_by(roi) %>%
  summarise_at(vars(r), list(name = mean))
```

```{r}
LIX_r_rlearn_sim_adole_social %>%
  group_by(roi) %>%
  summarise_at(vars(r), list(name = mean))
```



Monetary
Filter by group and task
```{r}
C1_r_social_sim_adole_mdoors <- C1_r_social_sim[(C1_r_social_sim$group == 'kid') & (C1_r_social_sim$task == 'mdoors'), ]
C1_r_rlearn_sim_adole_mdoors <- C1_r_rlearn_sim[(C1_r_rlearn_sim$group == 'kid') & (C1_r_rlearn_sim$task == 'mdoors'), ]
LIX_r_rlearn_sim_adole_mdoors <- LIX_r_rlearn_sim[(LIX_r_rlearn_sim$group == 'kid') & (LIX_r_rlearn_sim$task == 'mdoors'), ]
```



```{r}
C1_r_social_sim_adole_mdoors %>%
  group_by(roi) %>%
  summarise_at(vars(r), list(name = mean))
```

```{r}
C1_r_rlearn_sim_adole_mdoors %>%
  group_by(roi) %>%
  summarise_at(vars(r), list(name = mean))
```

```{r}
LIX_r_rlearn_sim_adole_mdoors %>%
  group_by(roi) %>%
  summarise_at(vars(r), list(name = mean))
```








## Being wins are different from loses and from negative wins
```{r}
all_sub_sim_val_win <- read.csv(file='corrval_rdm_similarity.csv', header = TRUE)
all_sub_sim_val_win
```


```{r}
ggplot(all_sub_sim_val_win, aes(x=roi, y=r, fill=task)) + 
  #stat_summary(fun.data=mean_sdl, geom='bar', position=position_dodge()) + 
  geom_bar(stat = 'summary', position=position_dodge()) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=90))
```





