---
title: "Univariate ROI Analysis"
author: "Haroon Popal"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: false
    df_print: paged
    css: !expr here::here("./style_srk_behavioral.css")
knit: (function(inputFile, encoding) { 
      out_dir <- './';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'srk_imaging_summary.html')) })
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

opts_knit$set(root.dir = "/Users/tuk12127/OneDrive - Temple University/olson_lab/projects/social_doors/derivatives/univariate_roi/")
```


```{r}
work_dir <- "/Users/tuk12127/OneDrive - Temple University/olson_lab/projects/social_doors/derivatives/univariate_roi/"
```

```{r}
library(psych)
```






```{r}
participants <- read.table(file='../derivatives/participants_good.tsv', sep = '\t', header = TRUE)
participants
```



```{r}
all_sub_roi_betas <- read.csv('../derivatives/univariate_roi/all_sub_roi_betas.csv')
all_sub_roi_betas$subject_id <- all_sub_roi_betas$subj
#all_sub_roi_betas <- subset(all_sub_roi_betas, select = -c(subj))

# Use "adult as group label
all_sub_roi_betas$group[all_sub_roi_betas$group == 'control'] <- 'college'


all_sub_roi_betas

```


# General ROI Response
Does the ROI activate for a given condition?

## Monetary condition - general feedback response

Create data subset for group and task
```{r}
adole_mdoors_data <- all_sub_roi_betas[(all_sub_roi_betas$group == 'kid') & (all_sub_roi_betas$task == 'mdoors'), ]
adult_mdoors_data <- all_sub_roi_betas[(all_sub_roi_betas$group == 'college') & (all_sub_roi_betas$task == 'mdoors'), ]
```


Create data subset for ROI
### Left VS - rlearn
```{r}
adole_mdoors_data_VS_l_rlearn <- subset(adole_mdoors_data, adole_mdoors_data$roi == 'VS_l-rlearn')
adult_mdoors_data_VS_l_rlearn <- subset(adult_mdoors_data, adult_mdoors_data$roi == 'VS_l-rlearn')
```

## T-Test
```{r}
win_data <- subset(adole_mdoors_data_VS_l_rlearn, adole_mdoors_data_VS_l_rlearn$outcome == 'win')
t.test(win_data$beta_mean, mu=0)
```

```{r}
win_data <- subset(adult_mdoors_data_VS_l_rlearn, adult_mdoors_data_VS_l_rlearn$outcome == 'win')
t.test(win_data$beta_mean, mu=0)
```

### Right Crus I - rlearn
```{r}
adole_mdoors_data_c1_r_rlearn <- subset(adole_mdoors_data, adole_mdoors_data$roi == 'region06-social')
adult_mdoors_data_c1_r_rlearn <- subset(adult_mdoors_data, adult_mdoors_data$roi == 'region06-social')
```

## T-Test
```{r}
win_data <- subset(adole_mdoors_data_c1_r_rlearn, adole_mdoors_data_c1_r_rlearn$outcome == 'win')
t.test(win_data$beta_mean, mu=0)
```

```{r}
win_data <- subset(adult_mdoors_data_c1_r_rlearn, adult_mdoors_data_c1_r_rlearn$outcome == 'win')
t.test(win_data$beta_mean, mu=0)
```


## Monetary condition - general feedback response

Create data subset for group and task
```{r}
adole_social_data <- all_sub_roi_betas[(all_sub_roi_betas$group == 'kid') & (all_sub_roi_betas$task == 'social'), ]
adult_social_data <- all_sub_roi_betas[(all_sub_roi_betas$group == 'college') & (all_sub_roi_betas$task == 'social'), ]
```


Create data subset for ROI
### Left VS - rlearn
```{r}
adole_social_data_VS_l_rlearn <- subset(adole_social_data, adole_social_data$roi == 'VS_l-rlearn')
adult_social_data_VS_l_rlearn <- subset(adult_social_data, adult_social_data$roi == 'VS_l-rlearn')
```

## T-Test
```{r}
win_data <- subset(adole_social_data_VS_l_rlearn, adole_social_data_VS_l_rlearn$outcome == 'win')
t.test(win_data$beta_mean, mu=0)
```

```{r}
win_data <- subset(adult_social_data_VS_l_rlearn, adult_social_data_VS_l_rlearn$outcome == 'win')
t.test(win_data$beta_mean, mu=0)
```

### Right Crus I - rlearn
```{r}
adole_social_data_c1_r_rlearn <- subset(adole_social_data, adole_social_data$roi == 'region06-social')
adult_social_data_c1_r_rlearn <- subset(adult_social_data, adult_social_data$roi == 'region06-social')
```

## T-Test
```{r}
win_data <- subset(adole_social_data_c1_r_rlearn, adole_social_data_c1_r_rlearn$outcome == 'win')
t.test(win_data$beta_mean, mu=0)
```

```{r}
win_data <- subset(adult_social_data_c1_r_rlearn, adult_social_data_c1_r_rlearn$outcome == 'win')
t.test(win_data$beta_mean, mu=0)
```


### Right Crus I - social
```{r}
adole_social_data_c1_r_social <- subset(adole_social_data, adole_social_data$roi == 'C1_r-social')
adult_social_data_c1_r_social <- subset(adult_social_data, adult_social_data$roi == 'C1_r-social')
```

## T-Test
```{r}
win_data <- subset(adole_social_data_c1_r_social, adole_social_data_c1_r_social$outcome == 'win')
t.test(win_data$beta_mean, mu=0)
```

```{r}
win_data <- subset(adult_social_data_c1_r_social, adult_social_data_c1_r_social$outcome == 'win')
t.test(win_data$beta_mean, mu=0)
```



## Social Reward
Mean beta ~ Outcome x ROI

Create data subset for group and task
```{r}
adole_social_data <- all_sub_roi_betas[(all_sub_roi_betas$group == 'kid') & (all_sub_roi_betas$task == 'social'), ]
adult_social_data <- all_sub_roi_betas[(all_sub_roi_betas$group == 'college') & (all_sub_roi_betas$task == 'social'), ]
```


Create data subset for positive valence
```{r}
adole_social_positive <- subset(adole_social_data, adole_social_data$valence == 'positive')
adult_social_positive <- subset(adult_social_data, adult_social_data$valence == 'positive')
```


Filter for ROIs
```{r}
adole_social_positive_rois <- adole_social_positive[(adole_social_positive$roi == 'VS_l-rlearn') | (adole_social_positive$roi == 'C1_r-rlearn'), ]
adult_social_positive_rois <- adult_social_positive[(adult_social_positive$roi == 'VS_l-rlearn') | (adult_social_positive$roi == 'C1_r-rlearn'), ]
```


ANOVA
```{r}
anova_adole_social <- aov(beta_mean ~ outcome*roi, data=adole_social_positive_rois)
summary(anova_adole_social)
```


```{r}
anova_adult_social <- aov(beta_mean ~ outcome*roi, data=adult_social_positive_rois)
summary(anova_adult_social)
```

```{r}
tukey.test <- TukeyHSD(anova_adole_social)
tukey.test
```


```{r}
tukey.test <- TukeyHSD(anova_adult_social)
tukey.test
```



# Social Reward between valence
mean_beta ~ valence x outcome x ROI

Filter for ROIs
```{r}
adole_social_roi <- adole_social_data[(adole_social_data$roi == 'VS_l-rlearn') | (adole_social_data$roi == 'C1_r-social'), ]
adult_social_roi <- adult_social_data[(adult_social_data$roi == 'VS_l-rlearn') | (adult_social_data$roi == 'C1_r-social'), ]
```


ANOVA
```{r}
anova_adole_social <- aov(beta_mean ~ valence*outcome*roi, data=adole_social_roi)
summary(anova_adole_social)
```





```{r}
anova_adult_social <- aov(beta_mean ~ valence*outcome*roi, data=adult_social_roi)
summary(anova_adult_social)
```


```{r}
ggplot(data=adole_social_roi, aes(x=roi, y=beta_mean, alpha=outcome, fill=valence)) + 
  geom_bar(stat = 'summary', position=position_dodge()) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=90))
```

```{r}
tukey.test <- TukeyHSD(anova_adole_social)
tukey.test
```






Create subsets for groups
```{r}
adole_data <- subset(all_sub_roi_betas,all_sub_roi_betas$group == 'kid')

adult_data <- subset(all_sub_roi_betas,all_sub_roi_betas$group == 'adult')

```

```{r}
adult_VS_l_rlearn <- subset(adult_data, adult_data$roi == 'VS_l-rlearn') 
```

```{r}
adole_VS_l_rlearn <- subset(adole_data, adole_data$roi == 'VS_l-rlearn') 
```

```{r}
anova_mod_adult <- aov(beta_mean ~ task*valence*outcome, data=adult_VS_l_rlearn)
summary(anova_mod_adult)
```

```{r}
ggplot(adult_VS_l_rlearn, aes(x=task, y=beta_mean, alpha=outcome, fill=valence)) + 
  stat_summary(fun.data=mean_sdl, geom='bar', position=position_dodge()) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=90))
```







```{r}
anova_mod_adole <- aov(beta_mean ~ task*valence*outcome, data=adole_VS_l_rlearn)
summary(anova_mod_adole)
```


Create subsets for the social and monetary tasks
```{r}
mdoors_data <- subset(all_sub_roi_betas,all_sub_roi_betas$task == 'mdoors')

social_data <- subset(all_sub_roi_betas,all_sub_roi_betas$task == 'social')

```

Create subsets for ROIs
```{r}
mdoors_VS_l_rlearn <- subset(mdoors_data, mdoors_data$roi == 'VS_l-rlearn') 
mdoors_VS_l_rlearn
```


```{r}
mdoors_C1_r_rlearn <- subset(mdoors_data, mdoors_data$roi == 'C1_r-rlearn') 
```

```{r}
mdoors_LIX_r_rlearn <- subset(mdoors_data, mdoors_data$roi == 'LIX_r-rlearn') 
```


# ANOVA

```{r}
anova_mod_mdoors <- aov(beta_mean ~ group*valence*outcome, data=mdoors_VS_l_rlearn)
summary(anova_mod_mdoors)
```


```{r}
anova_mod_mdoors <- aov(beta_mean ~ group*valence*outcome, data=mdoors_C1_r_rlearn)
summary(anova_mod_mdoors)
```


```{r}
anova_mod_mdoors <- aov(beta_mean ~ group*valence*outcome, data=mdoors_LIX_r_rlearn)
summary(anova_mod_mdoors)
```



```{r}
anova_mod_social <- aov(beta_mean ~ group*valence*outcome, data=social_data)
summary(anova_mod_social)
```


```{r}
ggplot(mdoors_LIX_r_rlearn, aes(x=group, y=beta_mean, fill=outcome)) + 
  stat_summary(fun.data=mean_sdl, geom='bar', position=position_dodge()) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=90))
```


```{r}
library(tidyverse)
library(haven)
library(psych)
library(reghelper)
library(sjPlot)
```


```{r}
cl5_m11_ss <- simple_slopes(ancova_mod)
cl5_m11_ss
```



```{r}
cell.means <- matrix(with(VS_l_data,
                          tapply(Beta, interaction(Valence, Domain), mean)))
cell.means
```







# Use Megan's data
```{r}
library('readxl')
library(dplyr)
library(stringr)
```


```{r}
full_data <- read_excel('../../misc/aggregate_full_data_SPSS_020419.xlsx')
full_data
```





```{r}
full_data$Subject <- gsub('s', 'sub-', full_data$Subject)
full_data
```


```{r}
VS_l_data$ch_totanx <- NA
VS_l_data$ch_cdi_total <- NA

for (subj in unique(VS_l_data$Subject_ID)) {
  VS_l_data[VS_l_data$Subject_ID == subj, ]$ch_totanx <- full_data[full_data$Subject == subj,]$ch_totanx
  VS_l_data[VS_l_data$Subject_ID == subj, ]$ch_cdi_total <- full_data[full_data$Subject == subj,]$ch_cdi_total
}
```


```{r}
ancova_mod <- aov(Beta ~ Domain*Valence*Outcome*ch_totanx*ch_cdi_total, data=VS_l_data)
anova(ancova_mod)
```


```{r}
ancova_mod <- lm(Beta ~ Domain*Valence*Outcome*ch_totanx*ch_cdi_total, data=VS_l_data)
summary(ancova_mod)
```


